Variation in Primary Care Prescribing in Wales due to COVID-19

### 2022-02-14 writing/paper.Rmd
New figures

gp_2020 <- read_rds("../data/gp_2020.rds")

@@

differences <- 
  furrr::future_map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
    mutate(.mean = mean(dist),
           drug = relevel(as_factor(drug), ref = "quant_all_drugs"))
plan(sequential)

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data"))
names(data_files) <-
  str_remove_all(list.files("../data/prescribing_data"), ".rds")
# 
# gp_extract <- 
#   map_dfr(.x = data_files[1:11],
#           .f = ~(read_rds(.x)),
#           .id = "drug")
```

@@

```{r}
monthlyPrescribing <- 
  function(data){
    data %>% 
      janitor::clean_names() %>% 
      mutate(datename = dmy(paste0("28-", datename)),
             practice_id = as.character(practice_id)) %>% 
      countRegional(practice_id, datename, quantity) %>% 
      mutate(year = year(datename)) %>%
      as_tibble() %>% 
      inner_join(gp %>% 
                   select(practice_id, year, npat), 
                 by = c("regional_unit" = "practice_id", "year")) %>% 
      mutate(n = 1000*n/npat,
             datename = yearmonth(datename),
             regional_unit = as_factor(regional_unit)) %>% 
      select(-c(npat, year)) %>% 
      as_tsibble(index = datename, key = regional_unit) %>% 
      fill_gaps()
  }

plan(cluster)
pres_2019 <- 
  data_files[c(1:10)] %>% 
  furrr::future_map(read_rds) %>% 
  furrr::future_map(monthlyPrescribing) %>% 
  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
  filter(year(datename) == 2019)
plan(sequential)

@@

differences_quantiles %>%
  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  dplyr::mutate(drug = case_when(drug == "quant_all_drugs" ~ "All",
                          drug == "ddd_ace" ~ "ACEi",
                          drug == "ddd_adreno" ~ "BAA",
                          drug == "ddd_cortico" ~ "Inhaled cortico",
                          drug == "ddd_hcq" ~ "HCQ",
                          drug == "ddd_nsaid" ~ "NSAIDs",
                          drug == "ddd_oral_contra" ~ "Oral contra",
                          drug == "ddd_paracet" ~ "Paracet",
                          drug == "ddd_ssri" ~ "SSRIs",
                          drug == "ddd_vitd" ~ "Vit D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All"),
         line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = line_type)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(text = element_text(size = 10),
        legend.position = c(1, 0),
        legend.justification = c(1, 0)) +
  scale_linetype_manual(values = c(2,1), name = " ") +
  xlab("Month") +
  ylab("Percentage difference from forecast dispensing")

ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", height = 14, width = 25, units = "cm")

differences_quantiles %>% 
  filter(datename == 3 & prop > 0 & 
           drug %in% c("quant_all_drugs", "ddd_ace", "ddd_adreno", 
                       "ddd_cortico", "ddd_hcq", "ddd_paracet", "ddd_ssri")) %>% 
  arrange(Percentile)

differences_quantiles %>% 
  select(-c(mean_prop, med_prop)) %>% 
  filter(datename == 5 & prop < 0) %>% 
  group_by(drug) %>% 
  count()

# Percentage of practices above or below forecast
differences %>% 
  na.omit() %>%
  dplyr::mutate(datename = month(datename),
         prop = 100*(prop - 1)) %>% 
  dplyr::group_by(datename, drug) %>% 
  summarise(high = round(100*sum(prop > 0)/n(),2),
            low = 100 - high) %>% 
  filter(datename == 6)

# Practice level variability
differences_quantiles %>% 
  pivot_wider(id_cols = datename:drug, names_from = Percentile, 
              values_from = prop) %>% 
  mutate(variability = `90%` - `10%`) %>% 
  select(-c(`10%`:`90%`)) %>% #filter(drug == "warfarin_ddd")
  ggplot(aes(x = datename)) +
  geom_line(aes(y = variability)) +
  facet_wrap(~drug)
```

@@

```{r, fig-2-single-fcts, eval=TRUE, fig.cap="Estimated percentage change [95% CI] from forecast dispensing. Grey line marks the level of forecast dispensing. Pink shading covers duration of Wales’ “stay at home” order. Please note the different y-axis scales across the plots. ACEi = ACE inhibitors, BAA = Beta~2~ adrenoceptor agonists, HCQ = Hydroxycholoroquine."}
plan(cluster)
nat_data <- # Data for all regional units combined
  data_files %>% 
  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
  filter(drug != "warfarin_ddd") %>% 
  dplyr::group_by(drug, datename) %>% 
  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  fill_gaps()

@@

#### Plot ####
best_model_discrep %>% 
  rename(drug = regional_unit) %>% 
  dplyr::mutate(datename = month(datename),
                datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8]),
                drug = case_when(drug == "quant_all_drugs" ~ "All",
                          drug == "ddd_ace" ~ "ACEi",
                          drug == "ddd_adreno" ~ "BAA",
                          drug == "ddd_cortico" ~ "Inhaled cortico",
                          drug == "ddd_hcq" ~ "HCQ",
                          drug == "ddd_nsaid" ~ "NSAIDs",
                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
                          drug == "ddd_paracet" ~ "Paracetamol",
                          drug == "ddd_ssri" ~ "SSRIs",
                          drug == "ddd_vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd_nat" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All"))%>% 
  group_by(drug) %>% 
  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
  ggplot(aes(x = datename, group = drug)) +
  geom_line(aes(y = med, col = drug)) +
  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, fill = drug), alpha = .3) +
  geom_hline(aes(yintercept = 0), col = "grey") +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  xlab("Month") +
  ylab("Percentage difference from forecast prescribing") +
  facet_wrap(~drug, scales = "free")

@@

#### Three month discreps ####
three_month_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(three_month_fcsts,  # Select best forecast
             by = c(".model", "regional_unit")) %>%
  left_join(nat_data %>% 
              filter(datename > yearmonth("2020 Feb") &
                       datename < yearmonth("2020 Jun")) %>% 
              as_tibble() %>% 
              select(-datename) %>% 
              ungroup() %>% 
              dplyr::group_by(regional_unit) %>% 
              dplyr::summarise(n = sum(n)),
            by = "regional_unit") %>% 
  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x))

@@

three_month_diffs <- 
  three_month_model_discrep %>% 
  mutate(pct_change = paste0(printnum(med), 
                             "[", printnum(ub_95), ",", 
                             printnum(lb_95), "]")) %>% 
  select(regional_unit, `Mar-May` = pct_change)

#### Joint table ####
three_month_diffs %>% 
  left_join(lockdown_diffs, by = "regional_unit") %>% 
  left_join(monthly_diffs, by = "regional_unit") %>% 
  kable(col.names = c("Drug", "Mar-May", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 8) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 10)) %>%
  landscape()

@@

```{r, gls-functions}
drugs <- unique(differences$drug)

@@

#### Collinearity diagnostics ####

colin <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  colin[[i]] <- vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
                        PC1 + PC2 + PC3 + PC4 + ngp + gp_load,
                      data = glsData(i)))
  options(datadist = NULL)
}

# colin # PC5 causing collinearity issues

#### GLS Analysis function ####
bestGLS <- function(data, k = 4, bootstrap = FALSE){
  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
  z <- vector("list", length(cp))

  ### Fit models
  for(k in 1:length(cp)){
    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
                    hboard + dispensing +
                    rcs(wimd2019, 4) + 
                    rcs(ngp, 4) + rcs(gp_load, 4) + 
                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                    rcs(PC4, 4) +
                    hboard:rcs(Month, 4:7) +
                    dispensing:rcs(Month, 4:7) +
                    rcs(wimd2019, 4):rcs(Month, 4:7) +
                    rcs(ngp, 4):rcs(Month, 4:7) +
                    rcs(gp_load, 4):rcs(Month, 4:7),
                  data = data,
                  correlation = cp[[k]](form = ~ Month | regional_unit))
  }

  arma_tab <- # Table for p and q values for corARMA()
    tibble(p = 1:3, 
           q = rep(0,3)) %>% 
    mutate(model = row_number() + length(cp))

  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
                 .f = ~ if(.x > 0 | .y >0)
                 { # p = 0 & q = 0 fails
                   tryCatch(
                     {gls(pct_change ~ rcs(Month, 4:7) +
                            hboard + dispensing +
                            rcs(wimd2019, 4) + 
                            rcs(ngp, 4) + rcs(gp_load, 4) + 
                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                            rcs(PC4, 4) +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            rcs(wimd2019, 4):rcs(Month, 4:7) +
                            rcs(ngp, 4):rcs(Month, 4:7) +
                            rcs(gp_load, 4):rcs(Month, 4:7),
                          data = data,
                          correlation = corARMA(form = ~ Month|regional_unit, 
                                                p=.x, q=.y))
                     },
                     error = function(cond){
                       message(paste("Model causing error: p = ", 
                                     .x, "q = ", .y))
                       message("Original error message:")
                       message(cond)
                       return(NULL)
                     },
                     warning = function(cond){
                       message(paste("Model causing warning: p = ", 
                                     .x, "q = ", .y))
                       message("Original warning message:")
                       message(cond)
                       return(NULL)
                     }
                   )
                 }))

  # Create table
  mod_comparison <- 
    bind_cols(metric = c("aic", "bic", "log_lik"), 
              bind_rows(aic,bic,log_lik)) %>% 
    pivot_longer(-metric) %>% 
    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
    rename(model = name) %>% 
    mutate(model = as.numeric(str_remove_all(model, "model")))

  ### Fit best model
  if(bootstrap == TRUE){  
    if(best_model_aic <= 6){
      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + 
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  cp[[best_model_aic]](form = ~ Month | regional_unit))
      }
    else{
      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + 
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  corARMA(form = ~ Month | regional_unit, 
                          p = filter(arma_tab, model == best_model_aic)$p, 
                          q = filter(arma_tab, model == best_model_aic)$q))
      }
  }
  else{
    if(best_model_aic <= 6){
      a <- Gls(pct_change ~ rcs(Month, 4:7) +
                 hboard + dispensing +  
                 rcs(wimd2019, 4) + 
                 rcs(ngp, 4) + rcs(gp_load, 4) + 
                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                 rcs(PC4, 4) + 
                 hboard:rcs(Month, 4:7) +
                 dispensing:rcs(Month, 4:7) +
                 rcs(wimd2019, 4):rcs(Month, 4:7) +
                 rcs(ngp, 4):rcs(Month, 4:7) +
                 rcs(gp_load, 4):rcs(Month, 4:7),
               data = data,
               correlation = 
                 cp[[best_model_aic]](form = ~ Month | regional_unit))
    }
    else{
      a <- Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + 
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
               data = data,
               correlation = 
                 corARMA(form = ~ Month | regional_unit, 
                         p = filter(arma_tab, model == best_model_aic)$p, 
                         q = filter(arma_tab, model == best_model_aic)$q))
    }
  }
  return(a)
}
```

@@

dd <- NULL
for(i in drugs){
  gls_data <- glsData(i)
  dd <- datadist(gls_data)
  options(datadist = "dd")
  best_gls <- bestGLS(gls_data)
  best_bs_gls <- bestGLS(gls_data, TRUE)
  rm(dd)
  best_models[[i]] <-
    best_gls
  best_bs_models[[i]] <- 
    best_bs_gls
  options(datadist = NULL)
}

@@

#### ANOVA Table ####
best_bs_models %>% 
  map(~anova(., tol = 1e-10)) %>% 
  map(~as_tibble(x = ., rownames = "Coef")) %>% 
  map(as.matrix) %>% 
  map(as_tibble) %>% 
  bind_rows(.id= "drug") %>% 
  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
  select(-c(`Chi-Square`, d.f.)) %>% 
  filter(!str_detect(Coef, "Nonlinear") &
           !str_detect(Coef, "TOTAL") &
           !str_detect(Coef,"All Interactions"),
         !str_detect(Coef, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
  pivot_wider(names_from = drug, values_from = P) %>% 
  mutate(across(ddd_ace:warfarin_ddd, ~printnum(., zero = FALSE)),
         Coef = str_remove_all(Coef, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
  select(Coef, quant_all_drugs, everything()) %>% 
  kable(booktabs = TRUE, linesep = "",
        caption = paste("Wald test p-values")) %>% 
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
  landscape()
```

>>>>

gp_2020 <- 
  read_rds("../data/gp_2020.rds") %>% 
  mutate(gp_load = npat/ngp)

quantile(gp_2020$wimd2019, 1/3)
quantile(gp_2020$wimd2019, 2/3)

gp_2020 <- 
  gp_2020 %>% 
  mutate(wimd2019 = case_when(wimd2019 <= 15.1 ~ 1,
                              wimd2019 > 27 ~ 3,
                              wimd2019 > 15.1 & wimd2019 <= 27 ~ 2),
         wimd2019 = factor(x = wimd2019, levels = 1:3,
                           labels = c("Low", "Med", "High")))

@@

differences <- 
  furrr::future_map_dfr(.x = differences_files,
                        .f = ~read_rds(paste0("../data/differences/", .x)),
                        .id = "drug") %>% 
  mutate(drug = relevel(as_factor(drug), ref = "quant_all_drugs"),
         drug = str_remove_all(drug, "ddd_"),
         drug = str_remove_all(drug, "quant_"),
         drug = str_remove_all(drug, "_ddd")) %>% 
  filter(regional_unit != "W95636") #https://abuhb.nhs.wales/news/news/important-information-regarding-lansbury-surgery-caerphilly/
plan(sequential)

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data"))
names(data_files) <-
  str_remove_all(list.files("../data/prescribing_data"), ".rds")
# 
# gp_extract <- 
#   map_dfr(.x = data_files[1:11],
#           .f = ~(read_rds(.x)),
#           .id = "drug")

# Functions

#### Summarise and standardise prescribing ####
monthlyPrescribing <- 
  function(data){
    data %>% 
      janitor::clean_names() %>% 
      mutate(datename = dmy(paste0("28-", datename)),
             practice_id = as.character(practice_id)) %>% 
      countRegional(practice_id, datename, quantity) %>% 
      mutate(year = year(datename)) %>%
      as_tibble() %>% 
      inner_join(gp %>% 
                   select(practice_id, year, npat), 
                 by = c("regional_unit" = "practice_id", "year")) %>% 
      mutate(n = 1000*n/npat,
             datename = yearmonth(datename),
             regional_unit = as_factor(regional_unit)) %>% 
      select(-c(npat, year)) %>% 
      as_tsibble(index = datename, key = regional_unit) %>% 
      fill_gaps()
  }

#### GLS Analysis function ####
bestGLS <- function(data, bootstrap = FALSE){
  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
  z <- vector("list", length(cp))

  ### Fit models
  for(k in 1:length(cp)){
    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                    gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
                  data = data,
                  correlation = cp[[k]](form = ~ Month | regional_unit))
  }

  arma_tab <- # Table for p and q values for corARMA()
    tibble(p = 1:2, 
           q = rep(0,2)) %>% 
    mutate(model = row_number() + length(cp))

  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
                 .f = ~ if(.x > 0 | .y >0)
                 { # p = 0 & q = 0 fails
                   tryCatch(
                     {gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                            gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
                          data = data,
                          correlation = corARMA(form = ~ Month|regional_unit, 
                                                p=.x, q=.y))
                     },
                     error = function(cond){
                       message(paste("Model causing error: p = ", 
                                     .x, "q = ", .y))
                       message("Original error message:")
                       message(cond)
                       return(NULL)
                     },
                     warning = function(cond){
                       message(paste("Model causing warning: p = ", 
                                     .x, "q = ", .y))
                       message("Original warning message:")
                       message(cond)
                       return(NULL)
                     }
                   )
                 }))

  # Create table
  mod_comparison <- 
    bind_cols(metric = c("aic", "bic", "log_lik"), 
              bind_rows(aic, bic, log_lik)) %>% 
    pivot_longer(-metric) %>% 
    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
    rename(model = name) %>% 
    mutate(model = as.numeric(str_remove_all(model, "model")))

  ### Fit best model
  if(bootstrap == TRUE){  
    if(best_model_aic <= 6){
      a <-  Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                  gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  cp[[best_model_aic]](form = ~ Month | regional_unit))
      }
    else{
      a <-  Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                  gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  corARMA(form = ~ Month | regional_unit, 
                          p = filter(arma_tab, model == best_model_aic)$p, 
                          q = filter(arma_tab, model == best_model_aic)$q))
      }
  }
  else{
    if(best_model_aic <= 6){
      a <- Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                 gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
               data = data,
               correlation = 
                 cp[[best_model_aic]](form = ~ Month | regional_unit))
    }
    else{
      a <- Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
                            wimd2019 + ngp + 
                 gp_load + PC1 + PC2 + PC3 + PC4 +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            wimd2019:rcs(Month, 4:7) +
                            ngp:rcs(Month, 4:7) +
                            gp_load:rcs(Month, 4:7),
               data = data,
               correlation = 
                 corARMA(form = ~ Month | regional_unit, 
                         p = filter(arma_tab, model == best_model_aic)$p, 
                         q = filter(arma_tab, model == best_model_aic)$q))
    }
  }
  return(a)
}

#### Percentiles for a given variable ####
percentiles <- function(data, var){
  # return vector of 5th, 25th, 50th, 75th, and 95th percentile
  var <- enquo(var)
  data %>% 
    summarise(enframe(stats::quantile(!!var, c(.05, .25, .5, .75, .95)), 
                      "Percentile", "value"), .groups = "drop") %>% 
    mutate(value = round(value)) %>% .$value
}

@@

```{r}
plan(cluster)
pres_2019 <- 
  data_files[c(1:10)] %>% 
  furrr::future_map(read_rds) %>% 
  furrr::future_map(monthlyPrescribing) %>% 
  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
  filter(year(datename) == 2019)
plan(sequential)

@@

differences_quantiles %>%
  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACEi",
                          drug == "cortico" ~ "Inhaled cortico",
                          drug == "hcq" ~ "HCQ",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "oral_contra" ~ "Oral contra",
                          drug == "paracet" ~ "Paracet",
                          drug == "sal" ~ "Salbutamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vit D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All"),
         line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = line_type)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(text = element_text(size = 10),
        legend.position = c(1, 0),
        legend.justification = c(1, 0)) +
  scale_linetype_manual(values = c(2,1), name = " ") +
  xlab("Month") +
  ylab("Percentage difference from forecast dispensing")

ggsave(filename = "Draft 5/Figures/Figure 2.png", device = "png", height = 14, width = 25, units = "cm")
```

@@

```{r, fig-2-single-fcts, eval=TRUE, fig.cap="Estimated percentage change [95% CI] from forecast dispensing. Grey line marks the level of forecast dispensing. Pink shading covers duration of Wales’ “stay at home” order. Please note the different y-axis scales across the plots. ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine."}
plan(cluster)
nat_data <- # Data for all regional units combined
  data_files %>% 
  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
  filter(drug != "warfarin_ddd") %>% 
  dplyr::group_by(drug, datename) %>% 
  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  fill_gaps()

@@

@@

@@

#### Joint table ####
lockdown_diffs %>% 
  left_join(monthly_diffs, by = "regional_unit") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 8) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()

@@

```{r, gls-functions, echo=FALSE}
drugs <- unique(differences$drug)

@@

#### Collinearity diagnostics ####
colin <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  colin[[i]] <- sum(vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
                        PC1 + PC2 + PC3 + PC4 + ngp + 
                          gp_load,
                      data = glsData(i))) >= 5)
  options(datadist = NULL)
}

# colin # no VIF >= 5
```

@@

dd <- NULL
for(i in drugs){
  gls_data <- glsData(i)
  gls_data %>% 
    mutate(hboard = as.factor(hboard),
           hboard = relevel(hboard, ref = "BC"))
  dd <- datadist(gls_data)
  options(datadist = "dd")
  best_gls <- bestGLS(gls_data)
  best_bs_gls <- bestGLS(gls_data, TRUE)
  rm(dd)
  best_models[[i]] <-
    best_gls
  best_bs_models[[i]] <- 
    best_bs_gls
  options(datadist = NULL)
}

@@

#### ANOVA Table ####
best_bs_models %>% 
  map(~anova(., tol = 1e-10)) %>% 
  map(~as_tibble(x = ., rownames = "Variable")) %>% 
  map(as.matrix) %>% 
  map(as_tibble) %>% 
  bind_rows(.id= "drug") %>% 
  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
  select(-c(`Chi-Square`, d.f.)) %>% 
  filter(!str_detect(Variable, "Nonlinear") &
           !str_detect(Variable, "TOTAL") &
           !str_detect(Variable,"All Interactions"),
         !str_detect(Variable, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
  pivot_wider(names_from = drug, values_from = P) %>% 
  mutate(across(ace:warfarin, ~printnum(., zero = FALSE)),
         Variable = str_remove_all(Variable, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
  select(Variable, all_drugs, everything()) %>% 
  kable(booktabs = TRUE, linesep = "",
        caption = paste("Wald test p-values")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
  landscape()
```

## Variation of impacts on dispensing

```{r, gls-fig-setup}
## Health board
drugs_hb <- c("all_drugs", "cortico", "nsaid", "oral_contra", "sal", "ssri", 
              "vitd", "warfarin")

## Dispensing status
drugs_disp <- c("all_drugs", "cortico", "paracet", "sal", "vitd")

## WIMD
drugs_wimd <- c("cortico", "sal", "ssri", "vitd")

## NGPs
drugs_ngp <- c("oral_contra", "sal")

## GP load
drugs_gpld <- c("oral_contra")

```{r, gp-2020-medians, include=FALSE}
gp_2020 %>% 
  dplyr::summarise(hboard = mode(hboard),
                   dispensing = mode(dispensing),
                   wimd2019 = mode(wimd2019),
                   ngp = median(ngp),
                   gp_load = median(gp_load),
                   PC1 = median(PC1),
                   PC2 = median(PC2),
                   PC3 = median(PC3),
                   PC4 = median(PC4))

```{r, gp-2020-percentiles, include=FALSE}
gp_2020_percentiles <- 
  data.frame(
    percentile = c(5, 25, 50, 75, 95),
    # wimd2019 = percentiles(gp_2020, wimd2019),
    ngp = percentiles(gp_2020, ngp),
    gp_load = percentiles(gp_2020, gp_load))
```

* Figures represent predicted changes to dispensing based on GLS models
* When considering the effect of a specific predictor over time, all other predictors will be set to the median value for continuous predictors and the mode for categorical predictors.
*

### Month

```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
dd <- NULL
gls_month_fig <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_month_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, 
            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
            conf.int = .95)

  options(datadist = NULL)
}

gls_month_fig %>% 
  map_dfr(as_tibble, .id = "drug") %>% 
  mutate(drug = as.factor(drug),
           drug = relevel(drug, ref = "all_drugs")) %>%
  ggplot(aes(x = Month, y = yhat)) +
  geom_line() +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) +
  facet_wrap(~drug, scales = "free_y")

* This is broadly a repeat of what is seen in Figure 2 and what is described in the text referring to that section, therefore will not be repeated here.

### Health board

```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
dd <- NULL
gls_hb_fig <- list()
for(i in drugs_hb){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_hb_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, hboard,
            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
            conf.int = .95)

  options(datadist = NULL)
}
